SST_patterns

### 2019-09-19 SST_patterns.Rmd
update
incomplete commit

OISST <- OISST %>% 
  select(lon, lat) %>% 
  mutate(product = "OISST")

CMC <- CMC %>% 
  select(lon, lat) %>% 
  mutate(product = "CMC")

sat_data <- rbind(CMC, OISST) %>% 
  rbind(., CMC) %>% 
  select(product, lon, lat)

@@

pixel_match <- sat_data %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match)

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products

# You will then have one time series for each product for each pixel at each distance for each site that you may then
# run the upwelling event function on
# You should do this via purrr::nest+map as you can see how much less code it requires
```

>>>>

# Decided to work with OISST and CMC as both has a time series of 30years
#

OISST_prod <- OISST %>% 
  select(lon, lat) %>% 
  mutate(product = "OISST")

CMC_prod <- CMC %>% 
  select(lon, lat) %>% 
  mutate(product = "CMC")

sat_data <- rbind(CMC_prod, OISST_prod) %>% 
  #rbind(., CMC) %>% 
  select(product, lon, lat)

@@

pixel_match <- sat_data %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match) %>% 
  unite(col = combi, lon, lat, sep = "/", remove = F)

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
# one time series for each product for each pixel at each distance for each site that you may then
dataset_filt <- function(df){
  filtered_products <- OISST %>% 
  unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
  filter(combi %in% pixel_match$combi)
}

OISST_fil <- dataset_filt(df = OISST)
CMC_fil <- dataset_filt(df = CMC)

# Repeat this on MODIS K10 and another time series of 10 years
